---
title: "The Report for Course Assignment Week 3"
author: "Pengfei LI"
date: "7/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Project Instruction

This assignment requires a web page presentation with a plot created with Plotly. The outcome report should be hosted on either Github Pages, RPubs, or NeoCities. The page should contain the data used to created the document and also a plot. Moreover, the report should fit the following review criteria:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?


# **Project Introduction**

There are two main stock market indices in USA, the Dow Jones Industrial Average Index and the NASDAQ Composite Index. They have deep influence on not only the domestic financial market and also the global market. Starting from 2006, both of them have experienced several waves of fluctuation due to various financial events. Here I presents the trends of these two indices.

# **Data**

The data is downloaded from the Thomas Routers Datastream database. The time horizon of these two datasets are 02/01/2006 to 07/01/2020, while the time frequency is daily. In the following section, a plot of indices price will be provided for the presentation of the indices trends.


# **Plot Processing

In this section, I shall present the plot processing procedure. 

## **Data Pre-processing**

First, it comes to the data pre-processing. The code is as follows.

```{r,echo=TRUE}
library(readxl)
library(dplyr)
library(plotly)

DJI <- read_excel("Price History.xlsx",
                  col_types = c("date","numeric","numeric","numeric"
                                ,"numeric","numeric","numeric","numeric"))
NAS <- read_excel("Price History_20200713_1152.xlsx",
                  col_types = c("date","numeric","numeric","numeric"
                                ,"numeric","numeric","numeric","numeric"))

price_index_DJI <- DJI%>%select(`Exchange Date`,Close)
price_index_NAS <- NAS%>%select(`Exchange Date`,Close)
price_index <- merge(price_index_DJI,price_index_NAS,by="Exchange Date")
price_index <- price_index%>%rename(Nasdaq=Close.x,DJI=Close.y)
head(price_index)
change_index <- merge(DJI%>%select(`Exchange Date`,`%Chg`),
                      NAS%>%select(`Exchange Date`,`%Chg`),by="Exchange Date")
change_index <- change_index%>%rename(Nasdaq=`%Chg.x`,DJI=`%Chg.y`)
head(change_index)
```

With the upper codes,the data is processed into the proper format. Then, it goes to the plotting procedure.

## **Plots**

1. The plots for the trends of two indices

```{r,echo=TRUE}
plot_1 <- plot_ly(price_index,x=~price_index$`Exchange Date`,y=~price_index$Nasdaq,
                  type = 'scatter',mode='lines',name = 'Nasdaq Index')
plot_1 <- plot_1%>%add_trace(y=~price_index$DJI,name='Dow Jones Index',mode='lines+markers')
plot_1 <- plot_1%>%layout(title="The trends of two stock indices", 
                          yaxis=list(title="Index Price"),
                          xaxis=list(title="Date"))
plot_1
```

2. The plots for the trends of volatility for two indices

```{r,echo=TRUE}
plot_2 <- plot_ly(change_index,x=~change_index$`Exchange Date`,
                  y=~change_index$Nasdaq,type = 'scatter',mode='lines',
                  name = 'Nasdaq volatility')
plot_2 <- plot_2%>%add_trace(y=~change_index$DJI,name='Dow Jones volatility',mode='lines+markers')
plot_2 <- plot_2%>%layout(title="The volatility of two stock indices", 
                          yaxis=list(title="Volatility Rate"),
                          xaxis=list(title="Date"))
plot_2
```