---
title: "The Report for Course Assignment Week 4"
author: "Pengfei LI"
date: "7/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Assignment Introduction**

This assignment project contains two parts:

## 1. **The Shiny Application**

### a. The overall requirement 

* Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application;
* Deploy the application on Rstudio's shiny server;
* Share the application link by pasting it into the provided text box;
* Share your server.R and ui.R code on github;

### b. The application must include the following:

* Some form of input (widget: textbox, radio button, checkbox, ...);
* Some operation on the ui input in sever.R;
* Some reactive output displayed as a result of server calculations;
* You must also include enough documentation so that a novice user could use your application;
* The documentation should be at the Shiny website itself. Do not post to an external link.

## 2. **Your Reproducible Pitch Presentation**

### a. The overall requirement 

* 5 slides to pitch our idea done in Slidify or Rstudio Presenter;
* Your presentation pushed to github or Rpubs;
* A link to your github or Rpubs presentation pasted into the provided text box;

### b. The presentation must satisfy the following

* It must be done in Slidify or Rstudio Presenter;
* It must be 5 pages;
* It must be hosted on github or Rpubs;
* It must contained some embedded R code that gets run when slidifying the document;


# **Project Design**

## *Project Aim*

This report is designed to present some further information relevant to the global financial market. There will be an application with several interactive plots inside. The plots are related to the stock market and other financial market all over the world. With different input, the plots will show the detailed information of these markets.

## *Project Data*

The data comes from the Thomson Reuters Database. It offers the data from 02/01/2006 to 07/01/2020. And the frequency of the data is daily. All the data files are in xlsx.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
